Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:


***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv("pseudo_facebook.tsv", sep="\t")

qplot(x = age, y = friend_count, data = pf)

```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

[All the ggplot geoms!](http://docs.ggplot2.org/current/)

```{r ggplot Syntax}

ggplot(aes(x = age, y = friend_count), data = pf) + geom_point()

summary(pf$age)

#xlim as additional layer

ggplot(aes(x = age, y = friend_count), data = pf) + geom_point() +
  xlim(13,90)

```

***

### Overplotting
Notes:

Overplotting is when it's difficult to tell how many points are in each region

```{r Overplotting}

ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha = 1/20) + #alpha to make stacked up dots visible
  xlim(13,90)

ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_jitter(alpha = 1/20) + #geom_jitter gets rid of some of the rigid columns
  xlim(13,90)

```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}

```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha = 1/20) + 
  xlim(13,90) + 
  coord_trans(y = "sqrt")

```

#### What do you notice?
It's rare for users over age 50 to have 0 friends, more common for young users, who also reach higher counts.
***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}

```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}

```

Create your plot!

```{r Conditional Means Plot}

```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}

```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(                 , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

