L3: The pseudofacebook data
===========================

```{r}
pf <- read.csv('pseudo_facebook.tsv', sep="\t")
names(pf)

library(ggplot2)

qplot(data=pf, x=dob_day) +
  scale_x_discrete(breaks=1:31)

qplot(data=pf, x=dob_day) +
  scale_x_discrete(breaks=1:31) +
  facet_wrap(~dob_month, ncol=3)
```

facet_wrap
----------
`facet_wrap` takes a formula `facet_wrap(formula)`. The formula is just a ~ followed by the (categorical) value you want to facet over. Above, it's months.

Similar: `facet_grid(formula)`: the formula is `(vertical~horizontal)`. Use this one for two or more variable situations.

##Friend count
```{r}
qplot(data = pf, x = friend_count)
```
Need to cut out long tail of data -- so use `xlim`:
```{r}
qplot(data = pf, x = friend_count, xlim = c(0,1000))
```
-or-
```{r}
qplot(data = pf, x = friend_count) +
  scale_x_continuous(limits = c(0,1000))
```

###Better labels and binning

```{r}
qplot(data = pf, x = friend_count, binwidth = 25) +
  scale_x_continuous(limits = c(0,1000), breaks = seq(0, 1000, 50))
```

###Histogram by gender
```{r}
qplot(data = subset(pf, !is.na(gender)), x = friend_count, binwidth = 25) +
  scale_x_continuous(limits = c(0,1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
```

##Statistics by gender
```{r}
table(pf$gender)

by(pf$friend_count, pf$gender, summary)
```
`by()` args: variable, categorical variable for faceting, function

##Tenure
```{r}
qplot(x = tenure, data = pf, binwidth = 30,
      color = I('black'), fill = I('#099DD9'))
```

###Tenure in years

```{r}
qplot(x = tenure/365, data = pf, binwidth = .25,
      color = I('black'), fill = I('#099DD9')) +
  scale_x_continuous(limits=c(0,7), breaks=seq(0,7,1))
```

##Labeling plots
```{r}
qplot(x = tenure/365, data = pf, binwidth = .25,
      xlab = "Years using FB",
      ylab = "Number of users",
      color = I('black'), fill = I('#099DD9')) +
  scale_x_continuous(limits=c(0,7), breaks=seq(0,7,1))
```

##User ages
```{r}
qplot(x = age, data = pf, binwidth = 1,
      xlab = "Age",
      ylab = "Number of users",
      color = I('#999999'), fill = I('#562267')) +
  scale_x_continuous(lim=c(0,113), breaks=seq(0,113,5))

qplot(x = age, data = pf, binwidth = 1,
      xlab = "Age",
      ylab = "Number of users",
      color = I('#999999'), fill = I('#562267')) +
  scale_x_discrete(breaks=seq(0,113,5))

```

##Transforming data
```{r}
qplot(x = friend_count, data = pf)

summary(pf$friend_count)

summary(log10(pf$friend_count + 1))

summary(sqrt(pf$friend_count))

install.packages("gridExtra")
library(gridExtra)

p1 = qplot(x = friend_count, data = pf)
p2 = qplot(x = (friend_count+1), data = pf) + scale_x_log10()
p3 = qplot(x = friend_count, data = pf) + scale_x_sqrt()

grid.arrange(p1,p2,p3, ncol=1)
```

##Frequency polygons
```{r}
qplot(x = friend_count, y = ..count../sum(..count..), 
      data = subset(pf, !is.na(gender)), binwidth=10, geom = 'freqpoly',
      color = gender) + 
  scale_x_continuous(lim = c(0,1000), breaks = seq(0,1000,50)) 
```

##Likes by gender
```{r}
summary(pf$likes)

qplot(x = www_likes, y = ..count../sum(..count..),
      data = subset(pf, !is.na(gender)), binwidth = 5, geom = 'freqpoly',
      color = gender) +
  scale_x_continuous(lim = c(0,100), breaks = seq(0,100,50))


```

