L3: The pseudofacebook data
===========================

```{r}
pf <- read.csv('pseudo_facebook.tsv', sep="\t")
names(pf)

library(ggplot2)

qplot(data=pf, x=dob_day) +
  scale_x_discrete(breaks=1:31)

qplot(data=pf, x=dob_day) +
  scale_x_discrete(breaks=1:31) +
  facet_wrap(~dob_month, ncol=3)
```

facet_wrap
----------
`facet_wrap` takes a formula `facet_wrap(formula)`. The formula is just a ~ followed by the (categorical) value you want to facet over. Above, it's months.

Similar: `facet_grid(formula)`: the formula is `(vertical~horizontal)`. Use this one for two or more variable situations.

##Friend count
```{r}
qplot(data = pf, x = friend_count)
```
Need to cut out long tail of data -- so use `xlim`:
```{r}
qplot(data = pf, x = friend_count, xlim = c(0,1000))
```
-or-
```{r}
qplot(data = pf, x = friend_count) +
  scale_x_continuous(limits = c(0,1000))
```

###Better labels and binning

```{r}
qplot(data = pf, x = friend_count, binwidth = 25) +
  scale_x_continuous(limits = c(0,1000), breaks = seq(0, 1000, 50))
```

###Histogram by gender
```{r}
qplot(data = subset(pf, !is.na(gender)), x = friend_count, binwidth = 25) +
  scale_x_continuous(limits = c(0,1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
```

##Statistics by gender
```{r}
table(pf$gender)

by(pf$friend_count, pf$gender, summary)
```
`by()` args: variable, categorical variable for faceting, function

##Tenure
```{r}
qplot(x = tenure, data = pf, binwidth = 30,
      color = I('black'), fill = I('#099DD9'))
```

###Tenure in years

```{r}
qplot(x = tenure/365, data = pf, binwidth = .25,
      color = I('black'), fill = I('#099DD9')) +
  scale_x_continuous(limits=c(0,7), breaks=seq(0,7,1))
```

